### 2019-09-03 paper/HOLMultivariate.tex
Updated all generated files

\newcommand{\HOLMultivariateDate}{20 Agosto 2019}
\newcommand{\HOLMultivariateTime}{13:05}

@@

       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{E}. \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}

@@

@@

\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map}. \HOLConst{CCS_Subst} \HOLConst{nil} \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_Subst} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_Subst} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E} \HOLBoundVar{rf}.
        \HOLConst{CCS_Subst} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X}.
        \HOLConst{CCS_Subst} (\HOLConst{var} \HOLBoundVar{X}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{THE} (\HOLConst{ALOOKUP} \HOLBoundVar{map} \HOLBoundVar{X})
        \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X} \HOLBoundVar{E}.
       \HOLConst{CCS_Subst} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=}
       \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}
       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsALOOKUPXXfromList}
       (\HOLConst{THE} (\HOLConst{ALOOKUP} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs})) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})

@@

\newcommand{\HOLMultivariateTheoremsALOOKUPXXfromList}{\UseVerbatim{HOLMultivariateTheoremsALOOKUPXXfromList}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSubstXXalt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} [(\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})]

@@

\newcommand{\HOLMultivariateTheoremsCCSXXSubstXXalt}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSubstXXalt}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}
       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLBoundVar{E})

@@

\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXELIM}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}}

>>>>

\newcommand{\HOLMultivariateDate}{03 Settembre 2019}
\newcommand{\HOLMultivariateTime}{10:42}

@@

       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}

@@

       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}

@@

\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
       \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

\newcommand{\HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}{\UseVerbatim{HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXsolutionXXlength}
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs})

@@

\newcommand{\HOLMultivariateTheoremsCCSXXsolutionXXlength}{\UseVerbatim{HOLMultivariateTheoremsCCSXXsolutionXXlength}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXelim}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXelim}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXelim}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{fm}. \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{FDOM} \HOLBoundVar{fm}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}). \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}) (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=}
        \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}. \HOLConst{CCS_Subst} \HOLBoundVar{e} \HOLBoundVar{y} \HOLBoundVar{x}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{IS_PROC} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXnested}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Es} \HOLBoundVar{C}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{C}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es}) \HOLBoundVar{C})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXnested}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXnested}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXnil}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXnil}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXnil}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXpar}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXpar}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXpar}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXprefix}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXprefix}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXprefix}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXPROC}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{P}.
       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{P}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{IS_PROC} \HOLBoundVar{P} \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXPROC}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXPROC}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrec}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrec}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrec}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXreduce}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps}.
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLBoundVar{X} \HOLConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}}
           (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
           (\HOLConst{CCS_SUBST} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLBoundVar{X})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXreduce}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXreduce}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrelab}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrelab}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrelab}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrestr}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrestr}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrestr}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXself}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
